A boundary-integral framework to simulate \\ the viscous erosion of a porous medium

### 2018-04-09 docs/methods/erosion_methods.tex
NM

Recent work in the high-Reynolds number regime has highlighted the importance of a shape-flow feedback that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann} and related processes such as dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.  In these cases, the flow alters the morphology of the immersed structures, which in turn modifies the surrounding flow, and so on. Such processes of `sculpting with flow' \cite{ristroph2018sculpting} have been examined in the context of a single body \cite{ris-moo-chi-she-zha2012} and, more recently, multiple bodies whose shape evolution is coupled through the flow \cite{hewett2017evolution, moore2017riemann}.
From this viewpoint, the example of an eroding porous medium presents new opportunities and challenges. First, since the medium is composed of many individual constituents, multi-body interactions must be considered. Second, the long-range effects inherent to Stokes flow implies that the shape-evolution of bodies are even more strongly coupled than they would be in any other regime.

@@

In closely related work, Mitchell \& Spagnolie used a traction integral equation formulation to simulate viscous erosion of a single body in three dimensions \cite{mit-spa2016}. Their formulation was flexible enough to simulate a {\em mobile} body that erodes in various background flows (uniform flow, shear flow, etc.). An advantage of the traction formulation is that is directly provides the shear stress that is needed to evolve surfaces.

Since our aim is to simulate porous-medium erosion, we will consider {\em many} bodies and, further,  we choose to fix these bodies to their initial locations. Thus, instead of a single, mobile body, we will consider multiple, immobile bodies.
Rather than the traction-formulation, we will employ a standard double-layer formulation which will easily allow us to compute bulk quantities such as pressure and vorticity as a post-processing step.

>>>>

Recent work in the high-Reynolds-number regime has highlighted the importance of a shape-flow feedback that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann} and related processes such as dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}.  In these cases, the flow alters the morphology of the immersed structures, which in turn modifies the surrounding flow, and so on. Such processes of `sculpting with flow' \cite{ristroph2018sculpting} have been examined in the context of a single body \cite{ris-moo-chi-she-zha2012} and, more recently, multiple bodies whose shape evolution is coupled through the flow \cite{hewett2017evolution, moore2017riemann}.
From this viewpoint, the example of an eroding porous medium presents new opportunities and challenges. First, since the medium is composed of many individual constituents, multi-body interactions must be considered. Second, the long-range effects inherent to Stokes flow implies that the shape-evolution of bodies are even more strongly coupled than in any other regime.

@@

In closely related work, Mitchell \& Spagnolie used a traction integral equation formulation to simulate viscous erosion of a single body in three dimensions \cite{mit-spa2016}. Their formulation was flexible enough to simulate a {\em mobile} body that erodes in various background flows (uniform flow, shear flow, etc.). An advantage of the traction formulation is that is directly provides the shear stress that is needed to evolve surfaces. 
%
Since our aim is to simulate porous-medium erosion, we will consider {\em many} bodies and, further,  we choose to fix these bodies to their initial locations. Thus, instead of a single, mobile body, we will consider multiple, immobile bodies.
Rather than the traction-formulation, we will employ a standard double-layer formulation which will easily allow us to compute bulk quantities such as pressure and vorticity as a post-processing step.
